% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{listings}
\newcommand{\passthrough}[1]{#1}
\lstset{defaultdialect=[5.3]Lua}
\lstset{defaultdialect=[x86masm]Assembler}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\subsubsection{\texorpdfstring{\textbf{Chapter 1: Information Systems in
Global Business
Today}}{Chapter 1: Information Systems in Global Business Today}}\label{chapter-1-information-systems-in-global-business-today}

\textbf{1. Which of the following is NOT one of the three major
technological trends in Management Information Systems mentioned in the
text?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Emerging mobile digital platform
\item
  Big Data
\item
  Cloud Computing
\item
  Artificial General Intelligence
\end{enumerate}

\textbf{Answer: D}

\textbf{2. A ``digital firm'' is characterized by which of the
following?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  High reliance on manual labor
\item
  Core business processes accomplished through digital networks
\item
  Centralized mainframe computing only
\item
  Local-only business relationships
\end{enumerate}

\textbf{Answer: B}

\textbf{3. Which of the following is NOT one of the six strategic
business objectives of information systems?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Operational Excellence
\item
  Improved Decision Making
\item
  Survival
\item
  Employee Surveillance
\end{enumerate}

\textbf{Answer: D}

\textbf{4. Raw facts representing events, such as bar code readings, are
defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Information
\item
  Knowledge
\item
  Data
\item
  Intelligence
\end{enumerate}

\textbf{Answer: C}

\textbf{5. Which three activities in an information system produce the
information organizations need?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Input, Processing, Output
\item
  Data, Software, Hardware
\item
  Analysis, Design, Implementation
\item
  Input, Storage, Deletion
\end{enumerate}

\textbf{Answer: A}

\textbf{6. Which dimension of information systems involves the physical
equipment used for input, processing, and output?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Organization
\item
  Management
\item
  Information Technology
\item
  Complementary Assets
\end{enumerate}

\textbf{Answer: C}

\textbf{7. In the organizational hierarchy, who is primarily responsible
for making long-range strategic decisions?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Operational Management
\item
  Middle Management
\item
  Senior Management
\item
  Knowledge Workers
\end{enumerate}

\textbf{Answer: C}

\textbf{8. Which discipline contributes to the technical approach to
information systems?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Sociology
\item
  Psychology
\item
  Computer Science
\item
  Economics
\end{enumerate}

\textbf{Answer: C}

\textbf{9. The ``sociotechnical systems'' perspective suggests that
optimal organizational performance is achieved by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Maximizing technology regardless of human needs
\item
  Focusing solely on employee happiness
\item
  Jointly optimizing both social and technical systems
\item
  Ignoring organizational structure
\end{enumerate}

\textbf{Answer: C}

\textbf{10. Assets required to derive value from a primary investment,
such as a supportive business culture, are called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Primary Assets
\item
  Complementary Assets
\item
  Depreciation Assets
\item
  Hidden Assets
\end{enumerate}

\textbf{Answer: B}

\textbf{11. Which company is mentioned as using handheld devices (DIAD)
and extensive IS for package tracking?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  FedEx
\item
  DHL
\item
  UPS
\item
  USPS
\end{enumerate}

\textbf{Answer: C}

\textbf{12. The Finnish company Ponsse is used as a case study for using
IS in which industry?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Automobile manufacturing
\item
  Wood harvesting/forestry
\item
  Mobile phone production
\item
  Shipping
\end{enumerate}

\textbf{Answer: B}

\textbf{13. What is the approximate annual growth rate of digital
information mentioned?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  1 terabyte
\item
  5 exabytes
\item
  10 petabytes
\item
  500 gigabytes
\end{enumerate}

\textbf{Answer: B}

\textbf{14. Which level of management typically monitors and controls
the business and makes mid-level decisions?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Senior Management
\item
  Middle Management
\item
  Operational Management
\item
  Data Workers
\end{enumerate}

\textbf{Answer: B}

\textbf{15. Feedback in an information system is defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The raw input data
\item
  The processing power of the CPU
\item
  Output returned to help evaluate or correct input
\item
  The electrical power consumption
\end{enumerate}

\textbf{Answer: C}

\textbf{16. Which of the following is an example of an Organizational
Complementary Asset?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Strong IS development team
\item
  Incentives for innovation
\item
  Internet infrastructure
\item
  Technology standards
\end{enumerate}

\textbf{Answer: A}

\textbf{17. Which of the following is an example of a Managerial
Complementary Asset?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Efficient business processes
\item
  Teamwork and collaboration environments
\item
  Technology service firms
\item
  Decentralized authority
\end{enumerate}

\textbf{Answer: B}

\textbf{18. The behavioral approach to information systems includes
which disciplines?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Computer Science, Operations Research, Physics
\item
  Sociology, Psychology, Economics
\item
  Management Science, Computer Science, Economics
\item
  Psychology, Mathematics, Operations Research
\end{enumerate}

\textbf{Answer: B}

\textbf{19. What does the ``Business Information Value Chain''
represent?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The cost of hardware
\item
  A series of value-adding activities for acquiring, transforming, and
  distributing information
\item
  The hierarchy of employees in a firm
\item
  The connection between suppliers and customers
\end{enumerate}

\textbf{Answer: B}

\textbf{20. According to the text, what percentage of the U.S. economy
depends on foreign trade?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  10\%
\item
  25\%
\item
  33\%
\item
  50\%
\end{enumerate}

\textbf{Answer: C}

\textbf{21. ``Time shifting'' in a digital firm refers to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Working in different time zones
\item
  Business operating 24/7
\item
  Delaying project deadlines
\item
  Recording meetings for later
\end{enumerate}

\textbf{Answer: B}

\textbf{22. ``Space shifting'' in a digital firm refers to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Moving to a larger office
\item
  Work taking place in a global workshop/location independent
\item
  Increasing storage space
\item
  Moving data to the cloud
\end{enumerate}

\textbf{Answer: B}

\textbf{23. Which business function is responsible for recruiting,
hiring, and training?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Finance \& Accounting
\item
  Sales \& Marketing
\item
  Human Resources
\item
  Manufacturing \& Production
\end{enumerate}

\textbf{Answer: C}

\textbf{24. The fundamental platform for a firm's information systems is
called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The Internet
\item
  IT Infrastructure
\item
  The World Wide Web
\item
  Big Data
\end{enumerate}

\textbf{Answer: B}

\textbf{25. Operations Research is a discipline associated with which
approach to IS?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Behavioral Approach
\item
  Technical Approach
\item
  Sociological Approach
\item
  Economic Approach
\end{enumerate}

\textbf{Answer: B}

\textbf{26. Which of the following is NOT a level in a firm's
hierarchy?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Senior Management
\item
  Middle Management
\item
  External Management
\item
  Operational Management
\end{enumerate}

\textbf{Answer: C}

\textbf{27. Data workers are distinct from knowledge workers because
they:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Create new knowledge
\item
  Process paperwork and data
\item
  Make strategic decisions
\item
  Perform physical labor
\end{enumerate}

\textbf{Answer: B}

\textbf{28. Which of the following is a strategic objective related to
meeting regulatory requirements?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Competitive Advantage
\item
  Survival
\item
  Customer Intimacy
\item
  New Products
\end{enumerate}

\textbf{Answer: B}

\textbf{29. The variation in returns on IT investment suggests that:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Investing in IT always guarantees high returns
\item
  IT investments never pay off
\item
  IT investments alone do not guarantee returns
\item
  The more you spend, the more you earn linearly
\end{enumerate}

\textbf{Answer: C}

\textbf{30. Mashaweer is a case study regarding a personal service
company in:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Finland
\item
  Egypt
\item
  USA
\item
  China
\end{enumerate}

\textbf{Answer: B}

\textbf{31. The term for converting raw input into a meaningful form
is:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Input
\item
  Output
\item
  Processing
\item
  Feedback
\end{enumerate}

\textbf{Answer: C}

\textbf{32. Who typically allocates human and financial resources in an
organization?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The IT department
\item
  Management
\item
  Production workers
\item
  Data entry clerks
\end{enumerate}

\textbf{Answer: B}

\textbf{33. The ``flattened world'' concept relates to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Reduced economic advantages due to the Internet/globalization
\item
  The physical shape of the earth
\item
  Flat organizational structures only
\item
  The decline of global trade
\end{enumerate}

\textbf{Answer: A}

\textbf{34. Operational Excellence is primarily driven by improving:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Employee salaries
\item
  Efficiency and productivity
\item
  Regulatory compliance
\item
  Public relations
\end{enumerate}

\textbf{Answer: B}

\textbf{35. Customer and Supplier Intimacy is a strategic objective
because:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  It lowers tax liability
\item
  Strong relationships lead to loyalty and repeat business
\item
  It allows for better surveillance
\item
  It creates more data to store
\end{enumerate}

\textbf{Answer: B}

\textbf{36. A system that helps a company outperformance competitors is
aiming for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Survival
\item
  Competitive Advantage
\item
  Operational Excellence
\item
  Compliance
\end{enumerate}

\textbf{Answer: B}

\textbf{37. Which discipline studies how human decision makers perceive
and use information?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Economics
\item
  Sociology
\item
  Psychology
\item
  Computer Science
\end{enumerate}

\textbf{Answer: C}

\textbf{38. Which discipline studies the production of digital goods and
market dynamics?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Economics
\item
  Sociology
\item
  Psychology
\item
  Operations Research
\end{enumerate}

\textbf{Answer: A}

\textbf{39. IT investments grew from 32\% to what percentage of all
invested capital between 1980 and 2011?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  42\%
\item
  52\%
\item
  62\%
\item
  72\%
\end{enumerate}

\textbf{Answer: B}

\textbf{40. The technical definition of an Information System
emphasizes:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Human behavior
\item
  Interrelated components collecting, processing, and distributing
  information
\item
  The cost of hardware
\item
  Political struggles in the office
\end{enumerate}

\textbf{Answer: B}

\textbf{41. Which of the following is considered a ``Social Asset''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Decentralized authority
\item
  Laws and regulations
\item
  Management culture
\item
  Business processes
\end{enumerate}

\textbf{Answer: B}

\textbf{42. Which component is NOT part of the sociotechnical view?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Technology
\item
  Organization
\item
  Mutual adjustment
\item
  Strict automation without human input
\end{enumerate}

\textbf{Answer: D}

\textbf{43. Apple's iPad and iPhone are examples of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Mainframe computing
\item
  The emerging mobile digital platform
\item
  Legacy systems
\item
  Stationery office equipment
\end{enumerate}

\textbf{Answer: B}

\textbf{44. ``Big Data'' refers to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Large physical hard drives
\item
  Analyzing huge volumes of data from web traffic and social media
\item
  The physical size of the internet
\item
  Government databases only
\end{enumerate}

\textbf{Answer: B}

\textbf{45. Software as a Service (SaaS) is associated with:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Cloud Computing
\item
  Local storage
\item
  Offline processing
\item
  Mainframe era
\end{enumerate}

\textbf{Answer: A}

\textbf{46. Which business function manages cash accounts and creates
financial statements?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Sales \& Marketing
\item
  Human Resources
\item
  Finance \& Accounting
\item
  Manufacturing
\end{enumerate}

\textbf{Answer: C}

\textbf{47. Production or service workers are responsible for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Making strategic plans
\item
  Producing the product and delivering service
\item
  Designing new products
\item
  Hiring staff
\end{enumerate}

\textbf{Answer: B}

\textbf{48. In the UPS case, the handheld computer used by drivers is
called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  iPad
\item
  DIAD (Delivery Information Acquisition Device)
\item
  GPS Tracker
\item
  SmartLog
\end{enumerate}

\textbf{Answer: B}

\textbf{49. An example of a ``New Business Model'' enabled by IS is:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A grocery store selling food
\item
  iTunes or Netflix
\item
  A bank offering savings accounts
\item
  A library lending books
\end{enumerate}

\textbf{Answer: B}

\textbf{50. Real-time data availability contributes most directly to
which strategic objective?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Survival
\item
  Improved Decision Making
\item
  Compliance
\item
  Supplier Intimacy
\end{enumerate}

\textbf{Answer: B}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{\texorpdfstring{\textbf{Chapter 2: Global E-business and
Collaboration}}{Chapter 2: Global E-business and Collaboration}}\label{chapter-2-global-e-business-and-collaboration}

\textbf{1. A set of logically related activities for accomplishing a
specific business result is called a:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Business Function
\item
  Business Process
\item
  Business Hierarchy
\item
  Business Unit
\end{enumerate}

\textbf{Answer: B}

\textbf{2. Which system type serves operational management by tracking
elementary activities and daily transactions?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  DSS
\item
  MIS
\item
  TPS
\item
  ESS
\end{enumerate}

\textbf{Answer: C}

\textbf{3. Which of the following is an example of a Transaction
Processing System (TPS)?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Executive Digital Dashboard
\item
  Payroll System
\item
  Voyage-Estimating System
\item
  Knowledge Management System
\end{enumerate}

\textbf{Answer: B}

\textbf{4. Systems that provide reports on current performance to middle
management are called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  TPS
\item
  MIS
\item
  ESS
\item
  CRM
\end{enumerate}

\textbf{Answer: B}

\textbf{5. Decision Support Systems (DSS) are best described as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Systems for routine, structured decisions
\item
  Systems for non-routine decisions using ``what-if'' analysis
\item
  Systems for senior executives to view dashboards
\item
  Systems for tracking daily sales
\end{enumerate}

\textbf{Answer: B}

\textbf{6. Which system serves senior management and focuses on
strategic issues and long-term trends?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  TPS
\item
  MIS
\item
  ESS
\item
  DSS
\end{enumerate}

\textbf{Answer: C}

\textbf{7. A ``Digital Dashboard'' is a feature typically found in:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  TPS
\item
  ESS
\item
  CRM
\item
  SCM
\end{enumerate}

\textbf{Answer: B}

\textbf{8. Systems that span functional areas and focus on executing
business processes across the firm are called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Departmental Applications
\item
  Enterprise Applications
\item
  Functional Systems
\item
  Local Applications
\end{enumerate}

\textbf{Answer: B}

\textbf{9. Which enterprise application integrates business processes
across manufacturing, accounting, finance, and HR into a single software
system?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  SCM
\item
  CRM
\item
  ERP (Enterprise Systems)
\item
  KMS
\end{enumerate}

\textbf{Answer: C}

\textbf{10. Supply Chain Management (SCM) systems focus on:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Managing relationships with customers
\item
  Managing relationships with suppliers
\item
  Internal employee knowledge
\item
  Executive decision making
\end{enumerate}

\textbf{Answer: B}

\textbf{11. Which system's objective is to optimize revenue, customer
satisfaction, and retention?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  SCM
\item
  ERP
\item
  CRM
\item
  KMS
\end{enumerate}

\textbf{Answer: C}

\textbf{12. Knowledge Management Systems (KMS) are designed to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Manage logistics
\item
  Capture and apply knowledge and experience
\item
  Process payroll
\item
  Track inventory levels
\end{enumerate}

\textbf{Answer: B}

\textbf{13. An internal company website accessible only by employees is
known as a(n):}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Extranet
\item
  Internet
\item
  Intranet
\item
  Ethernet
\end{enumerate}

\textbf{Answer: C}

\textbf{14. Company websites accessible to authorized vendors and
suppliers are called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Intranets
\item
  Extranets
\item
  Social Networks
\item
  Public Domains
\end{enumerate}

\textbf{Answer: B}

\textbf{15. Use of digital technology and the Internet to execute major
business processes is defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  E-commerce
\item
  E-business
\item
  E-government
\item
  Social Business
\end{enumerate}

\textbf{Answer: B}

\textbf{16. Buying and selling goods and services over the Internet is
defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  E-business
\item
  E-commerce
\item
  E-government
\item
  Collaboration
\end{enumerate}

\textbf{Answer: B}

\textbf{17. ``Social Business'' is characterized by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Top-down command structures
\item
  The use of social networking platforms to engage employees and
  customers
\item
  Strict prohibition of personal conversation
\item
  Offline team meetings
\end{enumerate}

\textbf{Answer: B}

\textbf{18. Which of the following is NOT a reason for the growing
importance of collaboration?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Changing nature of work
\item
  Emphasis on innovation
\item
  Decline in global presence
\item
  Growth of professional work
\end{enumerate}

\textbf{Answer: C}

\textbf{19. According to the McKinsey prediction, social technologies
could raise productivity of interaction workers by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  5-10\%
\item
  20-25\%
\item
  50\%
\item
  100\%
\end{enumerate}

\textbf{Answer: B}

\textbf{20. Which tool is classified as a ``Cyberlocker''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Skype
\item
  Dropbox
\item
  Facebook
\item
  Salesforce Chatter
\end{enumerate}

\textbf{Answer: B}

\textbf{21. Second Life is an example of which collaboration tool?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Wiki
\item
  Virtual World
\item
  Blog
\item
  Cyberlocker
\end{enumerate}

\textbf{Answer: B}

\textbf{22. Which Microsoft tool is described as browser-based
collaboration with document management and Version control?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Skype
\item
  SharePoint
\item
  Excel
\item
  Outlook
\end{enumerate}

\textbf{Answer: B}

\textbf{23. The ``Time/Space Collaboration Tool Matrix'' classifies
tools based on:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Cost and Speed
\item
  Same/Different Time and Same/Different Place
\item
  Audio vs.~Video
\item
  Internal vs.~External
\end{enumerate}

\textbf{Answer: B}

\textbf{24. The person in charge of information systems security is
the:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  CIO
\item
  CPO
\item
  CSO/CISO
\item
  CKO
\end{enumerate}

\textbf{Answer: C}

\textbf{25. The CKO is responsible for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Knowledge management programs
\item
  Security policy
\item
  Privacy laws
\item
  Hardware maintenance
\end{enumerate}

\textbf{Answer: A}

\textbf{26. Which job role acts as the principal liaison between the IS
group and the rest of the organization?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Programmer
\item
  Systems Analyst
\item
  Data Entry Clerk
\item
  CISO
\end{enumerate}

\textbf{Answer: B}

\textbf{27. ``IT Governance'' refers to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The software installed on government computers
\item
  Strategy and policies for using IT and assigning decision rights
\item
  The maintenance of hardware
\item
  The hiring of programmers
\end{enumerate}

\textbf{Answer: B}

\textbf{28. Which of the following is a benefit of Enterprise Systems?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Creating silos of information
\item
  Improving flexibility and coordination of business processes
\item
  Increasing manual data entry
\item
  Slowing down information flow
\end{enumerate}

\textbf{Answer: B}

\textbf{29. What is ``Telepresence''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A text-based chat system
\item
  High-quality integrated audio and visual environment for meetings
\item
  A file sharing protocol
\item
  An email server
\end{enumerate}

\textbf{Answer: B}

\textbf{30. The Schiphol International Hub case study focused on which
type of system?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Baggage handling system
\item
  Employee payroll
\item
  Customer loyalty program
\item
  Flight simulation
\end{enumerate}

\textbf{Answer: A}

\textbf{31. In the NTUC Income case study, the new system helped reduce
policy processing time by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  10\%
\item
  Half
\item
  90\%
\item
  It increased the time
\end{enumerate}

\textbf{Answer: B}

\textbf{32. Procter \& Gamble's ``Business Sphere'' is an example of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A transaction processing system
\item
  A decision support environment/room with large screens
\item
  A public website
\item
  A warehouse management system
\end{enumerate}

\textbf{Answer: B}

\textbf{33. Which of the following is an ``asynchronous'' collaboration
interaction (Different Time)?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Video conference
\item
  Instant Messaging
\item
  E-mail
\item
  Face-to-face meeting
\end{enumerate}

\textbf{Answer: C}

\textbf{34. Which position is responsible for compliance with data
privacy laws?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  CIO
\item
  CSO
\item
  CPO
\item
  CEO
\end{enumerate}

\textbf{Answer: C}

\textbf{35. Programmers are defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Liaisons between departments
\item
  Highly trained technical specialists who write software instructions
\item
  Managers of facility operations
\item
  Senior strategic planners
\end{enumerate}

\textbf{Answer: B}

\textbf{36. Salesforce Chatter and Microsoft Yammer are examples of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Enterprise Social Networking Tools
\item
  Spreadsheets
\item
  Hardware manufacturers
\item
  Legacy TPS
\end{enumerate}

\textbf{Answer: A}

\textbf{37. Which functional area deals with ``identifying customers''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Manufacturing
\item
  Sales and Marketing
\item
  Finance
\item
  Human Resources
\end{enumerate}

\textbf{Answer: B}

\textbf{38. Which functional area deals with ``checking quality''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Manufacturing and Production
\item
  Sales
\item
  Finance
\item
  HR
\end{enumerate}

\textbf{Answer: A}

\textbf{39. A ``Command and Control'' culture is characterized by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Horizontal communication
\item
  Top-down orders and no horizontal communication
\item
  Teams at all levels
\item
  Extensive social networking
\end{enumerate}

\textbf{Answer: B}

\textbf{40. A ``Collaborative'' culture is characterized by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Senior management establishing collaboration as vital
\item
  Strict vertical hierarchy
\item
  Information hoarding
\item
  Individual rewards only
\end{enumerate}

\textbf{Answer: A}

\textbf{41. Which system uses ``Input: Employee time sheet'' and
``Output: Paychecks''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Payroll TPS
\item
  Sales DSS
\item
  Executive Dashboard
\item
  CRM
\end{enumerate}

\textbf{Answer: A}

\textbf{42. Which system type is described as ``Not flexible'' and
having ``little analytical capability''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  DSS
\item
  MIS
\item
  ESS
\item
  Expert Systems
\end{enumerate}

\textbf{Answer: B}

\textbf{43. The ``Voyage-Estimating'' system is an example of a:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  TPS
\item
  MIS
\item
  DSS
\item
  ESS
\end{enumerate}

\textbf{Answer: C}

\textbf{44. ``Interorganizational systems'' automate the flow of
information:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Within a single department
\item
  Across organizational boundaries
\item
  Only to the CEO
\item
  Between the CPU and Hard Drive
\end{enumerate}

\textbf{Answer: B}

\textbf{45. Which of the following is a benefit of collaboration
regarding ``Quality''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  It makes work slower
\item
  Communicating errors and corrective actions faster
\item
  It reduces the need for meetings
\item
  It creates more paperwork
\end{enumerate}

\textbf{Answer: B}

\textbf{46. Which tool allows users to contribute and edit content on a
website without programming knowledge?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Wiki
\item
  Compiler
\item
  FTP client
\item
  Firewall
\end{enumerate}

\textbf{Answer: A}

\textbf{47. Google Drive is an example of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A legacy mainframe
\item
  A Cloud-based cyberlocker/collaboration tool
\item
  An on-premise server
\item
  A specialized DSS
\end{enumerate}

\textbf{Answer: B}

\textbf{48. Lotus Notes is cited as an early example of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Groupware
\item
  Social Media
\item
  CRM
\item
  ERP
\end{enumerate}

\textbf{Answer: A}

\textbf{49. The TELUS case study utilized which technology for social
learning?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Microsoft SharePoint
\item
  Oracle ERP
\item
  Custom Mainframe
\item
  Fax machines
\end{enumerate}

\textbf{Answer: A}

\textbf{50. Employment growth in IS/MIS jobs is projected to be:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  50\% lower than average
\item
  50\% greater than average
\item
  Flat (no growth)
\item
  Declining rapidly
\end{enumerate}

\textbf{Answer: B}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{\texorpdfstring{\textbf{Chapter 3: Information Systems,
Organizations, and
Strategy}}{Chapter 3: Information Systems, Organizations, and Strategy}}\label{chapter-3-information-systems-organizations-and-strategy}

\textbf{1. The ``technical'' definition of an organization focuses on:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Rights and privileges
\item
  Conflict resolution
\item
  Processing resources (capital/labor) into outputs
\item
  Cultural values
\end{enumerate}

\textbf{Answer: C}

\textbf{2. The ``behavioral'' definition of an organization emphasizes:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Production functions
\item
  Rights, privileges, obligations, and conflict resolution
\item
  Input/Output efficiency
\item
  Machine-like precision
\end{enumerate}

\textbf{Answer: B}

\textbf{3. Standard operating procedures in an organization are also
called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Politics
\item
  Routines
\item
  Culture
\item
  Constitutions
\end{enumerate}

\textbf{Answer: B}

\textbf{4. Divergent viewpoints about resource distribution in an
organization lead to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Organizational Politics
\item
  Efficiencies
\item
  Routines
\item
  Automation
\end{enumerate}

\textbf{Answer: A}

\textbf{5. ``Unassailable assumptions'' about what products to produce
and how constitute:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Organizational Culture
\item
  Business Processes
\item
  Politics
\item
  Environments
\end{enumerate}

\textbf{Answer: A}

\textbf{6. Technologies that radically change the business landscape
(e.g., car vs.~horse) are called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Routine Technologies
\item
  Disruptive Technologies
\item
  Sustaining Technologies
\item
  Legacy Technologies
\end{enumerate}

\textbf{Answer: B}

\textbf{7. Which Mintzberg organizational structure consists of a young,
small firm with an entrepreneur CEO?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Machine Bureaucracy
\item
  Divisionalized Bureaucracy
\item
  Entrepreneurial Structure
\item
  Adhocracy
\end{enumerate}

\textbf{Answer: C}

\textbf{8. Which structure is characterized by task force organizations
in rapidly changing environments?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Machine Bureaucracy
\item
  Professional Bureaucracy
\item
  Adhocracy
\item
  Divisionalized Bureaucracy
\end{enumerate}

\textbf{Answer: C}

\textbf{9. Transaction Cost Theory suggests that IT:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Increases the cost of market participation
\item
  Helps lower market participation costs (transaction costs)
\item
  Has no effect on costs
\item
  Makes firms grow larger in employee count
\end{enumerate}

\textbf{Answer: B}

\textbf{10. Agency Theory views the firm as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A happy family
\item
  A nexus of contracts among self-interested individuals
\item
  A machine for production
\item
  A political entity only
\end{enumerate}

\textbf{Answer: B}

\textbf{11. How does IT typically affect the number of middle managers?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Increases them significantly
\item
  Reduces them by empowering lower-level employees
\item
  Has no impact
\item
  Replaces them with senior managers
\end{enumerate}

\textbf{Answer: B}

\textbf{12. The most common reason for IS project failure is:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Hardware failure
\item
  Organizational/political resistance
\item
  Software bugs
\item
  Lack of electricity
\end{enumerate}

\textbf{Answer: B}

\textbf{13. Which of the following is NOT one of Porter's Five
Competitive Forces?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Traditional Competitors
\item
  New Market Entrants
\item
  Government Regulations
\item
  Substitute Products
\end{enumerate}

\textbf{Answer: C}

\textbf{14. Walmart's continuous replenishment system is an example of
which generic strategy?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Product Differentiation
\item
  Low-Cost Leadership
\item
  Market Niche Focus
\item
  Customer Intimacy
\end{enumerate}

\textbf{Answer: B}

\textbf{15. Nike's NIKEiD program is an example of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Low-Cost Leadership
\item
  Product Differentiation (Mass Customization)
\item
  Supplier Intimacy
\item
  Machine Bureaucracy
\end{enumerate}

\textbf{Answer: B}

\textbf{16. Hilton Hotels' OnQ System is used to support which
strategy?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Focus on Market Niche
\item
  Low-Cost Leadership
\item
  Generic manufacturing
\item
  Employee surveillance
\end{enumerate}

\textbf{Answer: A}

\textbf{17. ``Switching costs'' refer to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The cost of electricity
\item
  The cost/difficulty for a customer to switch to a competitor
\item
  The cost of networking switches
\item
  The price of a new computer
\end{enumerate}

\textbf{Answer: B}

\textbf{18. Which model highlights specific activities (Primary and
Support) where IS can add value?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Porter's Five Forces
\item
  The Value Chain Model
\item
  Agency Theory
\item
  Network Economics
\end{enumerate}

\textbf{Answer: B}

\textbf{19. In the Value Chain, ``Inbound Logistics'' is a:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Support Activity
\item
  Primary Activity
\item
  Secondary Activity
\item
  Tertiary Activity
\end{enumerate}

\textbf{Answer: B}

\textbf{20. In the Value Chain, ``Human Resources'' is a:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Primary Activity
\item
  Support Activity
\item
  Sales Activity
\item
  Logistics Activity
\end{enumerate}

\textbf{Answer: B}

\textbf{21. A ``Value Web'' is different from a traditional Value Chain
because it is:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Linear and rigid
\item
  A collection of independent firms synchronized by IT
\item
  Owned by a single firm
\item
  Paper-based
\end{enumerate}

\textbf{Answer: B}

\textbf{22. ``Synergy'' occurs when:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Output of units can be used as inputs to others, lowering costs
\item
  Firms compete aggressively
\item
  Costs increase due to complexity
\item
  Technologies fail
\end{enumerate}

\textbf{Answer: A}

\textbf{23. An activity for which a firm is a world-class leader is
called a:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Routine
\item
  Core Competency
\item
  Liability
\item
  Support Activity
\end{enumerate}

\textbf{Answer: B}

\textbf{24. Network Economics is characterized by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Diminishing returns
\item
  Marginal costs of adding users being near zero, while value grows
\item
  High costs for every new user
\item
  Decreasing value as size increases
\end{enumerate}

\textbf{Answer: B}

\textbf{25. A ``Virtual Company'' uses networks to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Avoid paying taxes
\item
  Link people and assets without traditional organizational boundaries
\item
  Create fake products
\item
  Simulate business in a game
\end{enumerate}

\textbf{Answer: B}

\textbf{26. In a Business Ecosystem, a ``Keystone firm'':}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Is a small niche player
\item
  Dominates the ecosystem and creates the platform (e.g., Microsoft,
  Walmart)
\item
  Is a supplier only
\item
  Does not use IT
\end{enumerate}

\textbf{Answer: B}

\textbf{27. Apple vs.~Samsung in the tablet market is an example of
competition between:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Individual products only
\item
  Business Ecosystems (Mobile Internet Platforms)
\item
  Local stores
\item
  Government agencies
\end{enumerate}

\textbf{Answer: B}

\textbf{28. American Airlines' SABRE system is an example of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A failed system
\item
  A classic strategic system that provided advantage
\item
  A non-strategic website
\item
  A payroll system
\end{enumerate}

\textbf{Answer: B}

\textbf{29. Research shows that successful alignment of IT with business
goals:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Is achieved by 100\% of firms
\item
  Leads to lower profitability
\item
  Explains about half of a firm's profits
\item
  Is not important
\end{enumerate}

\textbf{Answer: C}

\textbf{30. ``Benchmarking'' involves:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Guessing performance metrics
\item
  Comparing efficiency and effectiveness against strict standards
\item
  Ignoring competitors
\item
  Setting low goals
\end{enumerate}

\textbf{Answer: B}

\textbf{31. The ``Bullwhip effect'' is usually mitigated by:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Hiding information
\item
  Supply Chain Management systems
\item
  Increasing prices
\item
  Reducing quality
\end{enumerate}

\textbf{Answer: B} \emph{(Context implied in SCM discussion)}

\textbf{32. Which of the following is NOT a primary activity in the
Value Chain?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Operations
\item
  Sales and Marketing
\item
  Procurement
\item
  Service
\end{enumerate}

\textbf{Answer: C}

\textbf{33. Mass customization allows firms to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Produce identical products for everyone
\item
  Offer individually tailored products using mass production resources
\item
  Stop production entirely
\item
  Increase inventory costs
\end{enumerate}

\textbf{Answer: B}

\textbf{34. The ``Internet of Things'' (implied by connected
cars/sensors) helps:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Increase manual labor
\item
  Create new data streams for analysis and efficiency
\item
  Reduce internet usage
\item
  Discourage innovation
\end{enumerate}

\textbf{Answer: B}

\textbf{35. A ``Strategy of Survival'' implies:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Using IS because competitors/regulations force you to
\item
  Using IS to dominate the market
\item
  Using IS to increase prices
\item
  Using IS to shrink the company
\end{enumerate}

\textbf{Answer: A}

\textbf{36. Li \& Fung is an example of a:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Virtual Company
\item
  Machine Bureaucracy
\item
  Traditional Manufacturer
\item
  Keystone Firm
\end{enumerate}

\textbf{Answer: A}

\textbf{37. ``Best Practices'' are:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Theoretical ideas that never work
\item
  Solutions identified as the most successful for achieving objectives
\item
  Government laws
\item
  Examining the worst performing companies
\end{enumerate}

\textbf{Answer: B}

\textbf{38. The Law of Diminishing Returns usually applies to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Network Economics
\item
  Traditional Economics
\item
  Virtual Companies
\item
  Digital Goods
\end{enumerate}

\textbf{Answer: B}

\textbf{39. Sears' struggle against Walmart is attributed to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Lack of technology investment only
\item
  Damaged brand image and weak business model despite technology use
\item
  Too much inventory
\item
  High prices
\end{enumerate}

\textbf{Answer: B}

\textbf{40. Starbucks used ``Lean'' techniques and mobile platforms to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Increase wait times
\item
  Return to profitability and improve efficiency
\item
  Stop selling coffee
\item
  Eliminate all baristas
\end{enumerate}

\textbf{Answer: B}

\textbf{41. Ford's ``MyFord Touch'' is an example of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Low-cost leadership
\item
  Product Differentiation through software
\item
  Niche marketing
\item
  Supplier management
\end{enumerate}

\textbf{Answer: B}

\textbf{42. Which is a characteristic of ``Postindustrial
Organizations''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Authority based on position/hierarchy
\item
  Authority based on knowledge and competence
\item
  Strict vertical command
\item
  Focus on manual labor
\end{enumerate}

\textbf{Answer: B}

\textbf{43. Which factor is NOT cited as a reason for organizational
resistance?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Nature of IT innovation
\item
  Organization's structure
\item
  Color of the office walls
\item
  Tasks impacted by innovation
\end{enumerate}

\textbf{Answer: C}

\textbf{44. ``Efficient Customer Response Systems'' are most closely
linked to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Product Differentiation
\item
  Low-Cost Leadership (e.g., Walmart)
\item
  Niche Focus
\item
  HR Management
\end{enumerate}

\textbf{Answer: B}

\textbf{45. What happens when ``Substitute Products'' are high in an
industry?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Firms have more control over price
\item
  Firms have less control over price/profit margins
\item
  Monopoly is guaranteed
\item
  Customers have no choice
\end{enumerate}

\textbf{Answer: B}

\textbf{46. ``Strategic Transitions'' refer to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Updating software
\item
  Movement between levels of sociotechnical systems (changing goals,
  processes, etc.)
\item
  Moving office locations
\item
  Hiring a new CEO
\end{enumerate}

\textbf{Answer: B}

\textbf{47. Barnes \& Noble's Nook strategy was a response to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Regulatory changes
\item
  Disruptive technology (e-books)
\item
  Supplier demands
\item
  Employee strikes
\end{enumerate}

\textbf{Answer: B}

\textbf{48. In the ecosystem model, ``Niche firms'':}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Create the platform
\item
  Use the platform provided by the Keystone firm
\item
  Compete against the Keystone firm
\item
  Operate offline only
\end{enumerate}

\textbf{Answer: B}

\textbf{49. Flattening organizations generally results in:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Slower decision making
\item
  Faster decision making and broader span of control
\item
  More middle managers
\item
  Less data availability
\end{enumerate}

\textbf{Answer: B}

\textbf{50. The reciprocal relationship between organizations and
environments means:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  They do not affect each other
\item
  Organizations rely on environments, and can also influence them
\item
  Environments always destroy organizations
\item
  Organizations control environments completely
\end{enumerate}

\textbf{Answer: B}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{\texorpdfstring{\textbf{Chapter 4: Ethical and Social
Issues in Information
Systems}}{Chapter 4: Ethical and Social Issues in Information Systems}}\label{chapter-4-ethical-and-social-issues-in-information-systems}

\textbf{1. The ``Ripples in a Pond'' model illustrates:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The speed of internet connections
\item
  The relationship between ethical, social, and political issues
\item
  The cost of water cooling
\item
  The decline of hardware costs
\end{enumerate}

\textbf{Answer: B}

\textbf{2. Which of the following is NOT one of the Five Moral
Dimensions of the Information Age?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Information Rights and Obligations
\item
  System Quality
\item
  Hardware Speed
\item
  Accountability and Control
\end{enumerate}

\textbf{Answer: C}

\textbf{3. The trend that ``Computing power doubles every 18 months'' is
known as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Moore's Law (implied)
\item
  Metcalfe's Law
\item
  The Law of Diminishing Returns
\item
  The Storage Law
\end{enumerate}

\textbf{Answer: A} \emph{(Note: Text says ``Computing power doubles
every 18 months'', common knowledge aligns this with Moore's Law)}

\textbf{4. The use of computers to combine data from multiple sources to
create electronic dossiers is called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Networking
\item
  Profiling
\item
  Spying
\item
  Phishing
\end{enumerate}

\textbf{Answer: B}

\textbf{5. NORA stands for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Nonobvious Relationship Awareness
\item
  Network Organization Routing Algorithm
\item
  New Online Research Agency
\item
  No One Really Asks
\end{enumerate}

\textbf{Answer: A}

\textbf{6. ``Responsibility'' is defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Laws permitting recovery of damages
\item
  Accepting potential costs, duties, and obligations for decisions
\item
  Mechanisms to determine who took action
\item
  Being punished for a crime
\end{enumerate}

\textbf{Answer: B}

\textbf{7. ``Accountability'' refers to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Mechanisms to determine who took responsible action
\item
  The ability to pay for damages
\item
  A feature of political systems
\item
  Personal guilt
\end{enumerate}

\textbf{Answer: A}

\textbf{8. ``Liability'' is a feature of political systems that:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Allows individuals to recover damages done to them
\item
  Prevents all harm
\item
  Guarantees free speech
\item
  Monitors internet traffic
\end{enumerate}

\textbf{Answer: A}

\textbf{9. Which ethical principle states: ``Do unto others as you would
have them do unto you''?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Kant's Categorical Imperative
\item
  The Golden Rule
\item
  Utilitarian Principle
\item
  No Free Lunch Rule
\end{enumerate}

\textbf{Answer: B}

\textbf{10. Kant's Categorical Imperative suggests:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  If an action is not right for everyone, it is not right for anyone
\item
  Take the action that achieves the higher value
\item
  Do what feels right
\item
  Avoid all risk
\end{enumerate}

\textbf{Answer: A}

\textbf{11. The ``Slippery-Slope'' rule is formally known as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Descartes' Rule of Change
\item
  The Golden Rule
\item
  Risk Aversion Principle
\item
  Utilitarian Principle
\end{enumerate}

\textbf{Answer: A}

\textbf{12. The Utilitarian Principle advises to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Take the action that produces the least harm
\item
  Take the action that achieves the higher or greater value
\item
  Assume everything is owned
\item
  Do what everyone else does
\end{enumerate}

\textbf{Answer: B}

\textbf{13. The ``No Free Lunch'' Rule assumes:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Food should be free
\item
  All objects are owned by someone unless declared otherwise
\item
  Information is always free
\item
  Privacy does not exist
\end{enumerate}

\textbf{Answer: B}

\textbf{14. FIP stands for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Federal Internet Protocol
\item
  Fair Information Practices
\item
  Free Internet Policy
\item
  Fast Information Processing
\end{enumerate}

\textbf{Answer: B}

\textbf{15. Which is the ``Core Principle'' of FIP regarding disclosure
of practices?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Notice/Awareness
\item
  Security
\item
  Enforcement
\item
  Access
\end{enumerate}

\textbf{Answer: A}

\textbf{16. The ``Opt-In'' model of privacy means:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Businesses can collect info until the user says stop
\item
  Businesses are prohibited from collecting info unless the consumer
  specifically approves
\item
  No data can ever be collected
\item
  Data is collected anonymously
\end{enumerate}

\textbf{Answer: B}

\textbf{17. The ``Opt-Out'' model (used in the US) means:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Collection is permitted until the consumer requests it to stop
\item
  Collection is forbidden by default
\item
  Consumers must sign a waiver
\item
  Only government can collect data
\end{enumerate}

\textbf{Answer: A}

\textbf{18. Small text files deposited on a computer hard drive to track
visits are called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Web Beacons
\item
  Cookies
\item
  Spam
\item
  Trojans
\end{enumerate}

\textbf{Answer: B}

\textbf{19. Tiny software programs that keep a record of users' online
clickstreams (often invisible) are:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Cookies
\item
  Web Beacons (Web bugs)
\item
  Antivirus
\item
  Firewalls
\end{enumerate}

\textbf{Answer: B}

\textbf{20. Intellectual Property protects:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Tangible land
\item
  Intangible property created by individuals or corporations
\item
  Government buildings
\item
  Ocean waters
\end{enumerate}

\textbf{Answer: B}

\textbf{21. A ``Trade Secret'' protects:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Any intellectual work product used for business (formula, device,
  pattern) not in public domain
\item
  Only published books
\item
  Only patented machines
\item
  Public information
\end{enumerate}

\textbf{Answer: A}

\textbf{22. Copyright protects creators for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  20 years
\item
  Life of author plus 70 years (or 95 years for corps)
\item
  Forever
\item
  10 years
\end{enumerate}

\textbf{Answer: B}

\textbf{23. A Patent grants a monopoly on underlying concepts/ideas
for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  70 years
\item
  20 years
\item
  5 years
\item
  Indefinitely
\end{enumerate}

\textbf{Answer: B}

\textbf{24. The Digital Millennium Copyright Act (DMCA) makes it illegal
to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Buy software
\item
  Circumvent technology-based protections of copyrighted materials
\item
  Write code
\item
  Use the internet
\end{enumerate}

\textbf{Answer: B}

\textbf{25. Which forms of health risks are associated with computer
use?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  RSI, CVS, Technostress
\item
  Malaria, Flu
\item
  Broken bones
\item
  Sunburn
\end{enumerate}

\textbf{Answer: A}

\textbf{26. Carpal Tunnel Syndrome (CTS) is a type of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Computer Vision Syndrome
\item
  Repetitive Stress Injury (RSI)
\item
  Technostress
\item
  Virus
\end{enumerate}

\textbf{Answer: B}

\textbf{27. ``Technostress'' symptoms include:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Euphoria
\item
  Aggravation, hostility, impatience, fatigue
\item
  Better vision
\item
  Increased calmness
\end{enumerate}

\textbf{Answer: B}

\textbf{28. The ``Digital Divide'' refers to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The gap between Mac and PC users
\item
  The gap between those who have access to technology/Internet and those
  who do not
\item
  The split between hardware and software
\item
  Two separate hard drives
\end{enumerate}

\textbf{Answer: B}

\textbf{29. Most common source of business system failure is:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Hardware destruction
\item
  Data quality (input errors)
\item
  Hackers
\item
  Power outages
\end{enumerate}

\textbf{Answer: B}

\textbf{30. Which term refers to the commission of illegal acts through
the use of a computer?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Computer Abuse
\item
  Computer Crime
\item
  Hacking
\item
  Spamming
\end{enumerate}

\textbf{Answer: B}

\textbf{31. ``Spam'' accounts for approximately what percentage of
e-mail (2012 est)?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  10\%
\item
  72\%
\item
  99\%
\item
  25\%
\end{enumerate}

\textbf{Answer: B}

\textbf{32. In the context of privacy regulations, ``Safe Harbor'' is
defined as:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  A strict government-enforced law protecting ships
\item
  A private, self-regulating policy that meets objectives of government
  regulators without government regulation
\item
  A policy that completely bans data transfer between nations
\item
  A virus protection software for medical databases
\end{enumerate}

\textbf{Answer: B}

\textbf{33. European data protection laws are generally:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Less stringent than U.S. laws
\item
  More stringent than U.S. laws
\item
  Non-existent
\item
  Identical to U.S. laws
\end{enumerate}

\textbf{Answer: B}

\textbf{34. The ``Right to be forgotten'' is a concept proposed in:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  The United States
\item
  The European Union
\item
  China
\item
  Russia
\end{enumerate}

\textbf{Answer: B}

\textbf{35. Software that secretly installs itself to report user
movements is called:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Firmware
\item
  Spyware
\item
  Shareware
\item
  Freeware
\end{enumerate}

\textbf{Answer: B}

\textbf{36. Apple vs.~Samsung (2011) was a major battle over:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Copyrights
\item
  Patents
\item
  Trade Secrets
\item
  Trademarks
\end{enumerate}

\textbf{Answer: B}

\textbf{37. Which industry has a global software piracy rate of 42\%
(2011)?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Software
\item
  Music
\item
  Movies
\item
  Books
\end{enumerate}

\textbf{Answer: A}

\textbf{38. ``Cyberbullying'' is mentioned as a negative impact on:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  System Quality
\item
  Quality of Life (boundaries/social)
\item
  Intellectual Property
\item
  Accountability
\end{enumerate}

\textbf{Answer: B}

\textbf{39. Reengineering work has caused job losses primarily for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  CEOs
\item
  Mid-level managers and clerical workers
\item
  Doctors
\item
  Lawyers
\end{enumerate}

\textbf{Answer: B}

\textbf{40. CVS stands for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Computer Virus System
\item
  Computer Vision Syndrome
\item
  Central Vision System
\item
  Cardio-Vascular Stress
\end{enumerate}

\textbf{Answer: B}

\textbf{41. The BlackBerry outage (2011) highlights issues of:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Privacy
\item
  Accountability and Liability (who is responsible for economic harm?)
\item
  Intellectual Property
\item
  Patent theft
\end{enumerate}

\textbf{Answer: B}

\textbf{42. Which act bans deceptive email practices but has had minimal
impact?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  DMCA
\item
  CAN-SPAM Act
\item
  Patriot Act
\item
  Computer Fraud Act
\end{enumerate}

\textbf{Answer: B}

\textbf{43. The ``Risk Aversion Principle'' suggests avoiding:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Low-cost actions
\item
  High-failure-cost actions of moderate to high probability
\item
  All actions
\item
  Profitable actions
\end{enumerate}

\textbf{Answer: B}

\textbf{44. ``Due Process'' implies that:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Laws are known, understood, and there is an appeal ability
\item
  Punishment is immediate
\item
  There are no rules
\item
  Computers judge humans
\end{enumerate}

\textbf{Answer: A}

\textbf{45. Which company was fined \$160 million for manipulating LIBOR
rates?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Walmart
\item
  Barclays Bank
\item
  Siemens
\item
  Pfizer
\end{enumerate}

\textbf{Answer: B}

\textbf{46. Which company paid \$4 billion for a worldwide bribery
scheme?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Galleon Group
\item
  Siemens
\item
  GlaxoSmithKline
\item
  Apple
\end{enumerate}

\textbf{Answer: B}

\textbf{47. According to the key technology trends raising ethical
issues, the rapid decline in data storage costs means:} A) Less
databases are created

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\setcounter{enumi}{1}
\item
  Organizations can easily maintain detailed databases on individuals
\item
  Less privacy issues occur
\item
  Slower computers are used
\end{enumerate}

\textbf{Answer: B}

\textbf{48. What is the ``Golden Rule'' of Ethics?}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Make as much money as possible
\item
  Do unto others as you would have them do unto you
\item
  The one with the gold makes the rules
\item
  Survival of the fittest
\end{enumerate}

\textbf{Answer: B}

\textbf{49. Privacy is defined as the claim of individuals to:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Own data
\item
  Be left alone, free from surveillance
\item
  Speak freely
\item
  Access the internet
\end{enumerate}

\textbf{Answer: B}

\textbf{50. ``Look and feel'' distinctions in software are problematic
for:}

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\item
  Patents
\item
  Copyright protection
\item
  Trade Secrets
\item
  Hardware design
\end{enumerate}

\textbf{Answer: B}

\end{document}
